---
title: "Horror Movies"
output:
  pdf_document: default
  html_document: default
  word_document: default
date: "2023-08-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Installing the required packaged.
```{r, eval=FALSE}
install.packages("tidyverse")
install.packages("ggplot2")
install.packages("datapasta")
install.packages("ggpubr")
```

## R Markdown
```{r}
library(tidyverse)
library(ggplot2)
library(datapasta)
library(ggpubr)
```

Importing the datafile from local storage. Data is downloaded from TidyTuesday github repository.
```{r}
Horror_movies <- read.csv("horror_movies.csv")
```

Get a overview of the structure of our data
```{r}
str(Horror_movies)
```

We select the variables which is of interest. 
```{r}
sd_horror_movies <- Horror_movies %>% select("id","original_title","original_language","popularity","vote_average","budget","revenue")
```

We look at our subset data, and we can see that the languages are annotated with abbreviations. 
```{r}
str(sd_horror_movies)
```

To get the actual names of the language from the abbreviations we copy a table from this website: https://www.science.co.il/language/Codes.php and saved it into a new R-script. We converted it into a table. 
```{r}
lang <- data.table::fread("lang", data.table = FALSE, fill = TRUE)
```

We view our language data:
```{r}
head(lang)
```

Then we join our horror movie data with our language data, but only adding the Afar (language) column:
```{r}
joined_sd_horror_movies <- left_join(sd_horror_movies, lang, by=c("original_language"="aa")) %>% select(-"aar", -"afar")
```

Relocating Afar next original language column and renaming Afar to language:
```{r}
joined_sd_horror_movies <- joined_sd_horror_movies %>% relocate(Afar,.after="original_language") %>% rename(Language=Afar)
```

We arrange the data to find the top three language of the movies:
```{r}
joined_sd_horror_movies %>% group_by(Language) %>% summarise(Number=n()) %>% arrange(desc(Number))
```

Making a new dataset with only movies with a budget above 500.000(unit?), vote average above 1 and only of the top three language of movies:
```{r}
sd_horror_movies_w500000 <- joined_sd_horror_movies %>% filter(budget >= 500000, vote_average > 1, Language=="English"|Language=="Spanish; Castilian"|Language=="Japanese")
```

We examine whether a larger budget gives the movies a larger revenue by plotting scatter plot of budget vs. revenue for the three top language of movies(English, Japanese, Spanish) and linear regression:
```{r}

av_vote_revenue_d <- ggplot(sd_horror_movies_w500000, mapping=aes(x=budget, y=revenue, color=Language)) + geom_point() + scale_x_log10() + facet_grid(cols=vars(Language)) + geom_smooth(method="lm", formula=y~log(x), color="black", level=FALSE) + xlab("Budget (Log scale)") + ylab("Revenue") + ggtitle("Budget vs. Revenue") + theme_bw() 
av_vote_revenue_d 
```

We look into the linear regression for each the top three movie language estimating the R-squared and p-value to test the model fit. 
```{r}
lr1 <- sd_horror_movies_w500000 %>% group_by(Language) %>% do(model=lm(formula=revenue~log(budget), .))
lr1

summary(lr1[[2]][[1]])$coefficients

summary(lr1[[2]][[1]])$r.squared

summary(lr1[[2]][[2]])$coefficients

summary(lr1[[2]][[2]])$r.squared

summary(lr1[[2]][[3]])$coefficients

summary(lr1[[2]][[3]])$r.squared
```
Putting the R-squared and p-value for each group into a dataframe:
```{r}
dat_text <- data.frame(
  label = c("R = 0.247, p=0.001", "R = 0.298, p=0.001", "R = 0.070, p=0.144"),
  Language   = c("English", "Japanese", "Spanish; Castilian")
)
```

Adding the R-squared and p-value for each group into the figure:
```{r}

av_vote_revenue_d_wn <- ggplot(sd_horror_movies_w500000, mapping=aes(x=budget, y=revenue, color=Language)) + geom_point() + scale_x_log10() + facet_grid(cols=vars(Language)) + geom_smooth(method="lm", formula=y~log(x), color="black", level=FALSE) + xlab("Budget (Log scale)") + ylab("Revenue") + ggtitle("Budget vs. Revenue") + theme_bw() + geom_text(
  data    = dat_text,
  mapping = aes(x = 1e+05, y = 6.3e+08, label = label),
  hjust   = -0.1,
  vjust   = -1
)
av_vote_revenue_d_wn 
```
We have budget of the movies on X axis and its revenue on the Y axis. We looked into the top three language movies. Budget of movies in  all three language found to have a very low positive correlation with its revenue. However, only English and Japanese movies showed a significant correlation.


We examine whether a larger budget gives the movies a higher vote average by plotting scatter plot of budget vs. vote average for the three top language of movies(English, Japanese, Spanish) and linear regression:
```{r}
av_vote_budget_d <- ggplot(sd_horror_movies_w500000, mapping=aes(x=budget, y=vote_average, color=Language)) + geom_point() + scale_x_log10() + facet_grid(cols=vars(Language)) + geom_smooth(method="lm", color="black", level=FALSE) + xlab("Budget (Log scale)") + ylab("Vote average") + ggtitle("Budget vs. vote average") + theme_bw() 

av_vote_budget_d
```
We look into the linear regression for each the top three movie language estimating the R-squared and p-value to test the model fit. 
```{r}
lr2 <- sd_horror_movies_w500000 %>% group_by(Language) %>% do(model=lm(formula=vote_average~log(budget), .))
lr2

summary(lr2[[2]][[1]])$coefficients

summary(lr2[[2]][[1]])$r.squared

summary(lr2[[2]][[2]])$coefficients

summary(lr2[[2]][[2]])$r.squared

summary(lr2[[2]][[3]])$coefficients

summary(lr2[[2]][[3]])$r.squared
```

Putting the R-squared and p-value for each group into a dataframe:
```{r}
dat_text2 <- data.frame(
  label = c("R = 0.127, p=0.001", "R = 0.092, p=0.068", "R = 0.034, p=0.309"),
  Language   = c("English", "Japanese", "Spanish; Castilian")
)
```

Adding the R-squared and p-value for each group into the figure:
```{r}
av_vote_budget_d_wn <- ggplot(sd_horror_movies_w500000, mapping=aes(x=budget, y=vote_average, color=Language)) + geom_point() + scale_x_log10() + facet_grid(cols=vars(Language)) + geom_smooth(method="lm", color="black", level=FALSE) + xlab("Budget (Log scale)") + ylab("Vote average") + ggtitle("Budget vs. vote average") + theme_bw() + geom_text(
  data    = dat_text2,
  mapping = aes(x = 1e+05, y = 9, label = label),
  hjust   = -0.1,
  vjust   = -1
)

av_vote_budget_d_wn
```
We have budget of the movies on X axis and its vote average on the Y axis. We looked into the top three language movies. Budget of movies in  all three language found to have a very low positive correlation with its vote average. However, only English movies showed a significant correlation.

We examine whether larger budget movies has higher popularity by plotting scatter plot of budget vs. popularity for the three top language of movies(English, Japanese, Spanish) and linear regression:
```{r}
popu_budget_d <- ggplot(sd_horror_movies_w500000, mapping=aes(x=budget, y=popularity, color=Language)) + geom_point() + scale_x_log10() + facet_grid(cols=vars(Language)) + geom_smooth(method="lm", color="black", level=FALSE) + xlab("Budget (Log scale)") + ylab("Popularity") + ggtitle("Budget vs. popularity") + theme_bw()
popu_budget_d
```

We look into the linear regression for each the top three movie language estimating the R-squared and p-value to test the model fit. 
```{r}
lr3 <- sd_horror_movies_w500000 %>% group_by(Language) %>% do(model=lm(formula=popularity~log(budget), .))
lr3

summary(lr3[[2]][[1]])$coefficients

summary(lr3[[2]][[1]])$r.squared

summary(lr3[[2]][[2]])$coefficients

summary(lr3[[2]][[2]])$r.squared

summary(lr3[[2]][[3]])$coefficients

summary(lr3[[2]][[3]])$r.squared
```

Putting the R-squared and p-value for each group into a dataframe:
```{r}
dat_text3 <- data.frame(
  label = c("R = 0.048, p=0.001", "R = 0.016, p=0.459", "R = 0.132, p=0.041"),
  Language   = c("English", "Japanese", "Spanish; Castilian")
)
```

Adding the R-squared and p-value for each group into the figure:
```{r}
popu_budget_d_wn <- ggplot(sd_horror_movies_w500000, mapping=aes(x=budget, y=popularity, color=Language)) + geom_point() + scale_x_log10() + facet_grid(cols=vars(Language)) + geom_smooth(method="lm", color="black", level=FALSE) + xlab("Budget (Log scale)") + ylab("Popularity") + ggtitle("Budget vs. popularity") + theme_bw() + geom_text(
  data    = dat_text3,
  mapping = aes(x = 1e+05, y = 1550, label = label),
  hjust   = -0.1,
  vjust   = -1
)

popu_budget_d_wn
```
We have budget of the movies on X axis and its popularity on the Y axis. We looked into the top three language movies. Budget of movies in  all three language were found to have a very low positive correlation with its popularity. However, only English movies showed a significant correlation.

